---
title: "Regression and Time Series HW4"
author: "Yaniv Bronshtein"
date: "10/12/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Import the necessary libraries**
```{r}
library(tidyverse)
library(pls)
library(leaps)
```
**Read in csv**
```{r, echo=FALSE}
house <- read.table("/Users/yanivbronshtein/Coding/Rutgers/Regression_TimeSeries_Repo/data/housing_price.txt", header = TRUE)

```

(1) Based on the R output, what would be the regression model you suggest?
```{r}
model.prof <- lm(formula=Price~FLR+RMS+BDR+BTH+ST+GAR+FP+LOT,data=house)
summary(model.prof)
```
*Based on the output, I would suggest the model with Price as the dependent variable and*
*the features: FLR, RMS, BDR, ST, and FP based on the asterisks that R provides*
*in the summary() object and based on the actual p-values. I have provided the trained model.reduced.prof*
*that reflects this idea*



(2) Write down the full model and reduced model associated with the following test 
and draw a conclusion based on this test (Note: This is a row obtained from the R output):
GAR 1.77 1.40 1.26 0.2243
**Reduced model based on p-values from full model**
```{r}
model.reduced.prof <- lm(formula=Price~FLR+RMS+BDR+ST+FP, data=house)
summary(model.reduced.prof)
```


*H0: The coefficient for GAR is equal to 0*
*H1: The coefficient for GAR is significant and therefore non-zero*
*The F statistic is 26.05*
```{r}
model.prof.nogar <- lm(formula=Price~FLR+RMS+BDR+BTH+ST+FP+LOT,data=house)
anova(model.prof.nogar, model.prof)
```
*Based on the result of the anova, Pr(>F) is greater than 0.05, so we fail to*
*reject the null hypothesis with greater than 95% confidence. The F statistic is 1.5902*




(3) Write down the null hypothesis and alternative hypothesis associated with the F-statistic and
what is the conclusion based on the test.
*H0: The coefficients for BTH, GAR, and LOT are all equal to 0
*H1: There exists at least 1 coefficient the above features that is non-zero
```{r}
anova(model.prof, model.reduced.prof)

```

*For the reduced model we can reject H0 because of the high F statistic*

(4) The house for selling has 750 square feet of space, 5 rooms, 2 bedrooms, 
1.5 baths, storm windows, a 1-car garage, 1 fireplace and a 25 front-foot lot. 
Analyze the housing price data. Based on this dataset, what can you tell this 
person about how much he could expect to get for the house? Please report your 
fitted model and also construct a confidence interval for the prediction 
(Hint: You can try different variable selection methods to find the final model).

*We know the following coefficients:FLR=750, RMS=5, BDR=2, BTH=1.5, FP=1, LOT=25*

**Create a new dataframe with the specified coefficients to mimic a test set**
```{r}
test.df <- data.frame(FLR = 750, RMS = 5, BDR =2, BTH =1.5, ST =1, GAR =1, FP =1,LOT=25)
```

**Create the prediction**
```{r}
predict(model.prof,test.df, interval="confidence")

```

**Backward step-wise**
```{r}
reg.fit.bwd <- regsubsets(Price~FLR+RMS+BDR+BTH+ST+GAR+FP+LOT,data=house, method="backward")
reg.fit.bwd.sum <- summary(reg.fit.bwd)
```

**Get the min bic value for a conservative estimate**
```{r}
which.min(reg.fit.bwd.sum$bic)
```
#From the backward stepwise, we can remove BTH and GAR variables 

#Predicting based on the updated model 
```{r}
model.fit.using.bwd <- lm(formula=Price~FLR+RMS+BDR+ST+FP+LOT, data=house)
```
**Modified data**
```{r}
test.df2 = data.frame(FLR=750, RMS=5, BDR=2, ST=1, FP =1, LOT=25)
```
**Create the new prediction**
```{r}
predict(model.fit.using.bwd,test.df2, interval="confidence")
```
**Let's try the forward stepwise method now to see if our results differ**
```{r}
reg.fit.fwd <- regsubsets(Price~FLR+RMS+BDR+BTH+ST+GAR+FP+LOT,data=house, method="forward")
```

**Let's get the summary**
```{r}
reg.fit.bwd.sum <- summary(reg.fit.fwd)
reg.fit.bwd.sum
```

**Let's get the min BIC value**
```{r}
which.min(reg.fit.bwd.sum$bic)
```
*Both forward and backward selection concluded that the minimum number of features need*
*is 6 and the same features need to be removed. Thus the confidence intervals must also be*
*the same*




