---
title: "Yaniv Bronshtein HW1 Regression and Time Series"
author: "Yaniv Bronshtein"
date: "9/15/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Question 1

**(1)Create a column of y that includes 100 random sample from a normal**
**distribution with mean=10 and sd=1**
```{r}
set.seed(1)
y <- matrix(rnorm(n=100,mean=10, sd=1))
#(2) Create a column of x that includes numbers 1 to 100
x <- matrix(1:100)
#(3) Draw a scatter plot using R. Based on the figure, do you think
#x and y are correlated?
plot(x,y)
```

```{r}
corr <- cor(x,y)
corr
```
*Based on the plot and the result of cor(), I do not believe that x and y are*
*correlated. The value is -0.01456896 which is very close to 0*


**(4) Fit a regression model y = B_0 + B_1 * x + epsilon**
**and obtain the R^2 value.**
```{r}
lm_model <- lm(formula=y~x)
summary <- summary(lm_model)
r_sq <- summary$r.squared
r_sq
```

**(5)Fit a regression model y=??x + epsilon and obtain the R^2 value.*  
**Compare this R2 value with the one you have in (4) and** 
**explain which one is more reasonable.**  
**Which model you will recommend?**
```{r}
lm_model_2 <- lm(formula = y~x+0)
summary2 <- summary(lm_model_2)
r_sq2 <- summary2$r.squared
r_sq2
```

*The new R^2 is 0.7467852.*
*The new R^2 is much higher and according to standards,*
*is in a good range. If the R^2 had been significantly higher,*
*it would signal likely over-fitting. I would recommend the second model*
*as the first one suffers from under-fitting which explains why the R^2 is so*
*low. The sum of squared distance between the points and the regression line*
*is very high.*


**(6)  Based on the model that you recommend in (5), 
**is x an important factor to y?  Is this conclusion consistent with the 
**one you have in (3)?

```{r}
plot(x,y)
#Better model
abline(lm_model_2, col='red')
#Worse model
abline(lm_model, col='blue')
```
*Based on the model I recommended in (5), we still cannot tell if x is an*
*important factor to y because R^2 for the model is high while the correlation*
*calculated mathematically and observed visually in the plot shows* 
*inconsistency between (3) and (5)*
