---
title: "Time Series HW8"
author: "Yaniv Bronshtein(yb262)"
date: "11/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Import the necessary libraries**
```{r}
library(sarima)
library(forecast)
```
(III) For the following models, simulate 400 observations, estimate the model, obtain 1-step ahead to 12-step ahead predictions and their standard errors, and plot the last 24 observed observations with the predictions and their 95% confidence intervals.

1. $(x_t−20)=−0.7(x_{t−1}−20)+\epsilon_t,\epsilon_t ∼ N(0,5^2)$

```{r}
set.seed(123)
sim1 <- arima.sim(model=list(order=c(1,0,0), ar=c(-0.7)), n=400, sd = 5)+20
model1 <- arima(sim1, order=c(1,0,0))
model1.pred <- predict(model1, n.ahead=12)
```

**Predictions for model 1**
```{r}
model1.pred$pred
```

**Standard errors for model 1 predictions**
```{r}
model1.pred$se
```

**Plot last 24 observations with 95% confidence intervals for predictions **
```{r}
plot(forecast(model1,h=12, level=0.95), include=24)
```


2. $(1−1.4B+0.48B^2)(x_t−20)=(1+1.2B+0.35B^2)\epsilon_t,\epsilon_t ∼N(0,5^2)$
```{r}
set.seed(123)
sim2 <- arima.sim(model=list(order=c(2,0,2),ar=c(1.4,-0.48), ma=c(1.2,0.35)), n=400, sd=5)+20
model2 <- arima(sim2, order=c(2,0,2))
model2.pred <- predict(model2, n.ahead=12)
```

**Model 2 predictions**
```{r}
model2.pred$pred
```

**Standard errors for model 2 predictions**
```{r}
model2.pred$se
```

**Plot last 24 observations with 95% confidence intervals for predictions **
```{r}
plot(forecast(model2,h=12, level=0.95), include=24)
```





3. $(1−0.8B)\Delta x_t = (1+0.6B)\epsilon_t,\epsilon_t ∼ N(0,5^2)$
```{r}
set.seed(123)
sim3 <- arima.sim(model=list(order=c(1,1,1),ar=c(0.8), ma=c(0.6)), n=400, sd=5)
model3 <- arima(sim3, order=c(1,1,1))
model3.pred <- predict(model3, n.ahead=12)
```

**Model 3 predictions**
```{r}
model3.pred$pred
```

**Standard errors for model 3 predictions**
```{r}
model3.pred$se
```

**Plot last 24 observations with 95% confidence intervals for predictions **
```{r}
plot(forecast(model3,h=12, level=0.95), include=24)
```

4. $(1−B^{12})x_t =(1+0.8B)(1+0.8B^{12})\epsilon_t,\epsilon_t ∼N(0,5^2)$.

$ARIMA(0,0,1)(1,0,1)_{12}$
```{r}
set.seed(123)
sim4 <- sim_sarima(model=list(siorder=1, ma=c(0.8), sma=c(0.8), nseasons=12), n=400, sd=5)

model4 <- arima(sim4, order=c(0,0,1), seasonal=list(order=c(1,0,1), period=12))

model4.pred <- predict(model4, n.ahead=12)
```

**Model 4 predictions**
```{r}
model4.pred$pred
```

**Standard errors for model 4 predictions**
```{r}
model4.pred$se
```

**Plot last 24 observations with 95% confidence intervals for predictions **
```{r}
plot(forecast(model4,h=12, level=0.95), include=24)
```

