---
title: "Regression and Time Series:HW2"
author: "Yaniv Bronshtein"
date: "9/22/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
**Import the necessary libraries**
```{r}
library(tidyverse)
```

1. Calculate the market returns by taking the weighted average of columns 3 to 5, with weights 0.3, 0.4 and 0.3.
**Load in the data**
```{r}
data <- read_table("Portfolios_Formed_on_ME_eqW.txt")
```

**Calculate the weighted average**
```{r}
data <- data %>% mutate(market_returns=0.3*Lo30 + 0.4*Med40 + 0.3*Hi30)
```
(a) Plot the market return series `(plot(x,type=’l’)` will do).
```{r}
plot(x=data$date, y=data$market_returns, type='l')
```

(b) Comment on the features you see in the figure
*By setting the x-axis to date and y-axis to market_returns, one can see dramatic*
*Oscillation between prior to 1940 which was the start of WW2 war effort by the U.S*
*Looking at history, this was the time that the U.S came out of the Great Depression*
*In the years that followed, there were key events that caused severe drops,*
*but nothing like the stock market crash of 1929. Notable mentions are Black Monday(1987)*
*and the 2008 financial crisis*

2. Use the data from 1965.01 to 1969.12 (rows 463:522) only to fit a simple linear regression using Column 11 (the small company portfolio) as the response variable and the market return you obtained in (1) as explanatory variable. Answer the following questions:
```{r}
sub_df <- data[463:522,]
model.fit <- lm(formula = Lo10~market_returns, data = sub_df)
summary <- summary(model.fit)
summary
```


(a) Draw a scatter plot and add the estimated regression line to the plot.
**Extract the coefficients**
```{r}
coefs <- summary$coefficients
coefs

```

**Create plot and add abline**
```{r}
plot(x=sub_df$market_returns, y=sub_df[[11]], xlab = "Market Returns", ylab = "Lo10")
abline(model.fit, col='blue')
```
(b) What is the standard error of b1 for estimating $\beta_1$?
*The standard error for estimating* $\beta_1$ *is 0.06497297*
(c) Obtain a 95% confidence interval for b1. What does a confidence interval mean in general?
```{r}
confint(model.fit, 'market_returns', level=0.95)

```
*A confidence interval tells the statistician how stable the estimate is for the variable.* 
*A stable estimate means that if the experiment were performed again, a similar value would be computed*
(d) What is the p-value for testing H0 : $\beta_0 = 0$ vs H1 : $\beta_0 \ne 0$? What is your conclusion?

*Based on the summary from an earlier part, the P-value for the intercept $\beta_0$*
*is 8.396004e-02. The intercept is significant. We conclude that we must reject the null hypothesis*
*Thus the intercept cannot be 0*

(e) What is the p-value for testing H0 : $\beta_1 = 0$ vs H1 : $\beta_1 \ne 0$? What is your conclusion?
```{r}
model.fit3 <- lm(formula = Lo10~market_returns, data=sub_df)
summary3 <- summary(model.fit3)
summary3

```
*Because the P-value is small, we reject the H0. We can conclude there is a relationship between*
*market return and Lo10*
(f) Perform a 5% level test for testing H0 : $\beta_1 = 1$ vs H1 : $\beta_1 \ne 1$? What is your conclusion?
```{r}
model.fit4 <- lm(formula = Lo10~market_returns, data = sub_df)
summary_4 <- summary(model.fit4)
summary_4
```
```{r}
confint(model.fit4)
```
(g) Obtain the R2 of this linear regression model.fit. What does it mean? Comment on it.

```{r}

summary_4$r.squared

```
*The R^2 of the linear regression model.fit is 0 meaning that it does not explain any variance*
*The residuals are too large*


