---
title: "Regression and Time Series HW 3"
author: "Yaniv Bronshtein"
date: "9/28/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Import the necessary libraries**
```{r}
library(tidyverse)
library(leaps)
```
Use the IPOdecision data (0=withdraw) for the following analysis

(a) Fit a logistic regression model using all predictors in the data file. Comment on which
predictors are significant.

```{r}
df <- read.table("/Users/yanivbronshtein/Coding/Rutgers/Regression_TimeSeries_Repo/HW3/IPOdecision.dat", header = TRUE)
head(df,5)
```
**Fit a logistic regression**
```{r}

log.reg.fit <- glm(decision~., family=binomial("logit"), data=df)
summary(log.reg.fit)
```
*The features: debtRatio2, ProfibilityRatio, and Venture Dummy are the most significant*
*given the extremely low P-Values. However, debtRatio, DebtPaymentDummy, logMarket, and logAST are also signficant to a lesser degree*




b) Use backward selection procedure to find the (sub)optimal set of predictors to explain the IPO completion/withdrawn decision. Note: Backward selection starts with the largest model and remove the least significant predictor (largest p-value of the z-test) one by one, each time re-estimating the model, until all coefficients are significant at 5% level.


```{r}
bw.selection.fit <- regsubsets(decision~., method="backward", data=df )
bw.selection.summary <- summary(bw.selection.fit)
```
**Let us create a plot to determine the optimal set**


```{r}
par(mfrow=c(2,2))
plot(bw.selection.summary$adjr2, type='l', xlab='Dimension', ylab='Adjusted R^2')
plot(bw.selection.summary$cp, type='l', xlab='Dimension', ylab='Cp')
plot(bw.selection.summary$bic, type='l', xlab='Dimension', ylab='BIC')

```

*Based on the plots of the 3 metrics Adjusted R^2, Cp, and BIC, 4 dimensions is sufficient*
*to capture the data*
```{r}
bw.selection.summary


```
*Looking at the summary() object, the set of 4 predictors will contain the following features:*
*logAST, debtRatio, VentureDummy, logMarket* 


(c) Run an ANOVA analysis to compare the full model in (a) and the model you obtained in (b). 
Which one do you prefer? (Write the null hypothesis etc). 
Write down in detail the model you preferred, in mathematical equations.

```{r}

log.reg.fit2 <- glm(decision~logAST+debtRatio+VentureDummy+logMarket, family=binomial, data=df)

my_anova <- anova(log.reg.fit, log.reg.fit2, test='Chisq')
my_anova
```


*H0: All the beta coefficients for the features: logAST,debtRatio,VentureDummy,logMarket*
*are 0*
*H1: There exists at least one beta coefficient for the features mentioned in H0 that is non-zero*

*Based on the result of the test, the p-value obtained is less than 0.05 meaning there is evidence to suggest that at least one beta coefficient* 
*among logAST,debtRatio,VentureDummy,logMarket is non-zero.*
*Thus, the model with all the variables is a better model because it has at least one of the features missing from the reduced model*
$y = 1.17211*logAST + -3.24485*debtRatio - 56.36229*debtRatio2 +$ 
$51.98373*Profitability + 1.60128*VentureDummy-0.09156*underwriterRating +$ 
$0.14882*logRevenue - 1.08411*DebtPaymentDummy - 1.31368*logMarket +$ 
$5.56798*NASDAQ30dayReturn - 0.31168*logNumIPS + 19.32453$

