---
title: "hw5"
author: "Yaniv Bronshtein"
date: "11/6/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Import the necessary libraries
```{r}
library(forecast)#Source of gold dataset
library(tryCatchLog) #For exception handling
library(TTR) #For SMA
```

Daily morning gold prices in US dollars. 1 January 1985 – 31 March 1989.
```{r}
data("gold")
```
The classic Box & Jenkins airline data. Monthly totals of international airline passengers, 1949 to 1960 from base-R datasets. Monthly data.
```{r}
data(AirPassengers)
```

A time series object containing average air temperatures at Nottingham Castle in degrees Fahrenheit for 20 years.(1920-1939)
```{r}
data(nottem)
```


**Create time series objects from data**
```{r}
gold_ts <- ts(gold, start=1, end = 731) #January 1st 1985- Jan 1st 1987 subset
air_pass_ts <- AirPassengers
nottem_ts <- ts(nottem)

```

**Plot gold time series**
```{r}
plot.ts(gold_ts)
```

**Plot Air Passengers time series **
```{r}
plot.ts(air_pass_ts)
```

**Plot nottem time series**
```{r}
plot.ts(nottem_ts)
```
**Decomposing Gold time series.Impossible, so there is no seasonal component **
```{r}
try_catch(decomposed_gold_additive <- decompose(gold_ts, type='additive'), .e=~print("Cannot decompose additive agold"))
try_catch(decomposed_gold_mult <- decompose(gold_ts, type='multiplicative'), .e=~print("Cannot decompose multiplicative gold"))
```
**Instead, let us try to use SMA for Gold data.**
```{r}
try_catch(sma_gold <- SMA(gold_ts), .e=~print("Cannot get moving average gold"))
```
**We can now try exponential smoothing on gold data**
```{r}
log_gold <- log(gold_ts)
#Now that we have taken the log, let's try to fit a linear model
plot.ts(log_gold)
```

**Decomposing Airpassenger time series.Successful**
```{r}
try_catch(decomposed_air_pass_additive <- decompose(air_pass_ts, type='additive'), .e=~print("Cannot decompose additive air pass"))
try_catch(decomposed_air_pass_mult <- decompose(air_pass_ts, type='multiplicative'), .e=~print("Cannot decompose multiplicative air pass"))

```

**Since Airpassenger decomposition was successful, let us plot the decomposed version.**
**We see that both plots are successful.**
```{r}
plot(decomposed_air_pass_additive)
plot(decomposed_air_pass_mult)
```
**Let us now try seasonal adjustment for AirPassengers**
```{r}
air_pass_seasonal_adj <- air_pass_ts - decomposed_air_pass_additive$seasonal
plot(air_pass_seasonal_adj)
```

**Decomposing Nottem time series.Impossible **
```{r}
try_catch(decomposed_nottem_additive <- decompose(nottem_ts, type='additive'), .e=~print("Cannot decompose additive nottem"))
try_catch(decomposed_nottem_mult <- decompose(nottem_ts, type='multiplicative'), .e=~print("Cannot decompose multiplicative nottem"))
```
**Instead, let us try to use SMA for Nottem data**
```{r}
try_catch(sma_nottem <- SMA(nottem_ts), .e=~print("Cannot get moving average SMA"))
```

**Since no error was generated, we can plot sma_nottem**
```{r}
plot.ts(sma_nottem)
```

# Observations and Conclusions
In the subset of data taken from the gold prices dataset, the price of Gold is increasing.
That is not the case for the entire dataset.
Neither Gold nor nottem data are additive models which is why decompose() 
does not work for them. 

However, Air passengers is additive and multiplicative as both decompositions are possible
There is a clear upward trend; As time increases, the number of passengers increases
For nottem data, we were able to compute the moving average using SMA().


